Leader functions and qualities across 59 cultures: an exploratory analysis

### 2019-12-01 leadership_across_cultures_contexts.Rmd
Fixed bib entry.
Added paragraphy in discussion.

@@

The most common benegits associated with leadership are material resources, increased social status, and social services (See Figure \@ref(fig:varsupportcb)). Measures of material and social wealth coupled with reproductive success represent a feature of leadership qualities descriptive of benefits of social influence and high social status (Figure \@ref(fig:cluster)A, *Material, social, & reproductive success* cluster $AU = 96$.).

>>>>

<!-- Qualities features -->

@@

The most common benefits associated with leadership are material resources, increased social status, and social services (See Figure \@ref(fig:varsupportcb)). Measures of material and social wealth coupled with reproductive success represent a feature of leadership qualities descriptive of benefits of social influence and high social status (Figure \@ref(fig:cluster)A, *Material, social, & reproductive success* cluster $AU = 96$.).

<!-- Functions features -->

Results suggest X features of the functions of leaders. Leaders may serve various prosocial functions, such as providing subsistence and distributing resources, they may be tasked with providing hospitality services to guests or followers, they function to protect the group via a variety of behaviors, and very commonly are leading in various social functions tied to cultural values and social practices (Figure \@ref(fig:cluster)B, *Prosocial* cluster $AU = 95$).
